I. Data munge
========================================================
Started: Linggi Sept 23,2013   

notes:    
text in *italic* indicates response to test   
text in **Bold** indicates things to note or follow up on   

### Purpose
1.Perform initial preprocessing steps to get rid of any errors in data gathering or collection.  
2.Perform quality checks      

executed: `r date() `
  
input, raw .xls file 'ws'    
output, ws.preprocessed    
Set path to data folder

```{r}
setwd('/Volumes/Documents-1/R_onAir/EGF_gage analysis')
require(XLConnect)

#import data, in .xls form.
ws=readWorksheetFromFile('/Volumes/Documents-1/R_onAir/EGF_gage analysis/data/Seq02_density.xls',sheet=1,header=T, rownames=1)
```
### What is the response variable? 

```{r} 
check.resopnse.var=print(summary(ws))
  response.var.answer = 'Gene expression level, Z-scale normalized ' ### manual input#*
```
### Is it categorical or continuous?

```{r}
   ### 
   cat.or.cont.answer = print('continuous') ### manual input#*
```
### What is the range of values?

```{r} 
response.var.range = print(range(ws$low.none.none,na.rm=T))
```
#### Are there any outliers?

```{r}
   response.boxplot = boxplot(ws)
```
*answer: some outliers in a couple of samples, but is not too dramatic. keep them there*   ### manual input  
 
```{r}
# do not use    ws.v2 = ws[- which(ws$Fold.Change==(max(ws$Fold.Change,na.rm=TRUE))),]
```
recheck for other outliers
```{r}
 #do no use response.boxplot.v2 = boxplot(ws.v2$Fold.Change)
```

#### Are there any missing values? Should they be removed?

```{r}
summary.ws.v2 = print(summary(ws))
```
*1 nan in each column
`r which(is.na(ws[,12])) `
*each is at row 15070. is last row*
`r ws[15070,] `
*remove this row*
`r ws= ws[-15070,] `

*also remove any rows that have 'na' names, there are 1282*
`r ws= ws[-(grep('na.',rownames(ws), ignore.case=F)),]`
*also remove rows with names with ####, there are 25 *
`r ws= ws[-(grep('###',rownames(ws), ignore.case=F)),] `

*the new dataset has `r (nrow(ws)) ` rows


### Determine data coding 
*not necessary for this dataset, no factors to code*    

#```{r}
 data.coding.workbook=loadWorkbook('../diagnostics/levels.xls',create=TRUE)
     createSheet(data.coding.workbook,name='coding_levels')
     description=paste((date()),'diagnostics: LEVELS of column data')
     writeWorksheet(description,object=data.coding.workbook, sheet='levels', startRow=1,header=F)
     writeWorksheet(t(colnames(ws.v2)),object=data.coding.workbook, sheet='levels', startRow=3, startCol=2)
 
 for (i in  1:ncol(ws)){
        #output all levels for factors
           writeWorksheet(levels(as.factor(ws.v2[,i])), object= data.coding.workbook,sheet='levels',startCol=i+1,startRow=5,header=F)
                             }
          saveWorkbook(data.coding.workbook)
 ```
 look at 'levels.xls' in /diagnostics to determine if coding is appropriate  

             
# #### Recode variables    

  ```{r}
 #ws.v2.factored=ws.v2
       # make vector to id all columns to factor except response variable
       idx=1:ncol(ws.v2)
       idx = idx[-21]  # idx of response var
    for (i in idx)
     {
      ws.v2.factored[,i] = as.factor(ws.v2[,i])
     }
```
#### Make new sheet in same .xls sheet and export summary

 ```{r}
 createSheet(data.coding.workbook,name='levels_summary')
       writeWorksheet(summary(ws.v2.factored),object=data.coding.workbook,sheet='levels_summary')
       saveWorkbook(data.coding.workbook)
       # and print to console
       print(summary(ws.v2.factored))
```

#### Output of this step of preprocessing

```{r}
ws.prepocessed = ws
save.image('/Volumes/Documents-1/R_onAir/EGF_gage analysis/diagnostics/Preproc.Rdata')

