Gage pipeline, Step I- calcs
========================================================
Started: Bryan Linggi October 2, 2013  
Updated:  
Input: Preprocessed data. 'Preproc.Rdata' from 'diagnostics'  
Output: results of gage      

[link to Gage manuscript](http://www.biomedcentral.com/1471-2105/10/161) 


### Get pathway library   
if is new pathway library, make in separate script and test
```{r}
setwd('/Volumes/Documents-1/R_onAir/EGF_gage analysis/')

require("gage")

data(go.gs)
data(kegg.gs)
data(egSymb)
# make library generic for next steps
path.lib =  kegg.gs #kegg.gs
# convert entrez to sym

path.lib = lapply(path.lib,eg2sym)
```

### Import data from preproccessing folder
```{r} 
load('/Volumes/Documents-1/R_onAir/EGF_gage analysis/tests/init_analysis_output.Rdata')

# make data generic for next steps
# WARNING: row names and data must be correct for the next line

#for this data, need to get rid of bracketint " ' "
 row.names(ws)= sub('\'','',sub('\'','',row.names(ws)))
data.G1 = as.matrix(ws) 

#identify control and test column for comparison
control.idx = grep('high.ctrl.none',colnames(data.G1),ignore.case=T)
test.idx = grep('high.egf.none',colnames(data.G1),ignore.case=T)
#check
check.control =print(colnames(data.G1)[control.idx])
check.treatment = print(colnames(data.G1)[test.idx])
```
** gernalized from here on **

#### Gage analysis
```{r}
#options: called answers
ans.same.dir = F
ans.use.fold = F # or F is t-statistic
ans.rank.test = F
ans.ref = control.idx
ans.samp = test.idx
ans.saaTest = gs.KSTest # non-parametric
ans.use.stouffer= T # p-value normalization method
ans.compare = 'unpaired' # 'paired', 'unpaired', '1ongroup','as.group'

analysis.1 <- gage(data.G1, gsets = path.lib, ref = ans.ref, samp = ans.samp, same.dir=ans.same.dir, use.fold= ans.use.fold, rank.test= ans.rank.test, saaTest = ans.saaTest, compare= ans.compare, use.stouffer=ans.use.stouffer)

# to select essential genes in group# these are used in KeggVis.Rmd for pathway viewing
analysis.esg.greater <- esset.grp(analysis.1$greater, data.G1, gsets=path.lib, ref = ans.ref, samp = ans.samp, output = F,make.plot = F, compare= ans.compare, test4up= T, samedir=ans.same.dir, use.fold=ans.use.fold)

analysis.esg.less <- esset.grp(analysis.1$less, data.G1, gsets=path.lib, ref = ans.ref, samp = ans.samp, output = F,make.plot = F, compare= ans.compare, test4up= T, samedir=ans.same.dir, use.fold=ans.use.fold)

```
### output
#### text output to /report location. change name as necessary

```{r} 
# output primary analysis data results to file, TODO, create labels

write.table(rbind(analysis.1$greater), file = '/Volumes/Documents-1/R_onAir/EGF_gage analysis/tests/out.xls', sep ="\t") 
```

#save to allow load for next steps
```{r}
save.image('/Volumes/Documents-1/R_onAir/EGF_gage analysis/tests/gageS1_output.Rdata ')
```


