Gage pipeline, Step I- calcs
========================================================
Started: Bryan Linggi October 2, 2013  
Updated:  
Input: Preprocessed data. 'Preproccessing.Rdata' from 'munge' fold  
Output: results of gage      

[link to Gage manuscript](http://www.biomedcentral.com/1471-2105/10/161) 

`r require(gage) `

### Get pathway library   
if is new pathway library, make in separate script and test
```{r}
setwd('~/Documents/R_onAir/GageAnalysis/reports/')
data(kegg.gs)
# make library generic for next steps
path.lib = kegg.gs
```

### Import data
```{r} 
load('~/Documents/R_onAir/GageAnalysis/munge/Preprocessed.Rdata')
# make data generic for next steps
# WARNING: row names and data must be correct for the next line
data.G1 = as.matrix(ws[,2:13]) 
#identify control and test column for comparison

control.idx = grep('HN',colnames(data.G1),ignore.case=T)
test.idx = grep('DCIS',colnames(data.G1),ignore.case=T)
#check
check.control =print(colnames(data.G1[control.idx]))
check.treatment = print(colnames(data.G1[test.idx]))
```
** gernalized from here on **

#### Gage analysis
```{r}
#options: called answers
ans.same.dir = F
ans.use.fold = T # or F is t-statistic
ans.rank.test = T
ans.ref = control.idx
ans.samp = test.idx
ans.saaTest = gs.KSTest # non-parametric
ans.sam = 'unpaired' # or 'paried'
ans.use.stouffer= T # p-value normalization method
ans.compare = 'paired' # 'paired', 'unpaired', '1ongroup','as.group'

analysis.1 <- gage(data.G1, gsets = kegg.gs, ref = ans.ref, samp = ans.samp, same.dir=ans.same.dir, use.fold= ans.use.fold, rank.test= ans.rank.test, saaTest = ans.saaTest, compare= ans.compare, use.stouffer=ans.use.stouffer)
```
### output
#### text output to /report location. change name as necessary

```{r} 
# output data results to file
write.table(analysis.1$greater, file = '~/Documents/R_onAir/GageAnalysis/reports/test_sample_gage.xls', sep ="\t") `

#### create heatpam, heatmap-sends to local /reports folder
 summary.regulated = sigGeneSet(analysis.1, heatmap=1, pdf.size=c(8,8), qpval= 'q.val',  cutoff=.01) #TODO change formatting of heatmap
```

### identify gene sets (pathways) that overlap in their core genes   
Core gene sets are those that contribute most to the identification of the gene set as signifiant   

# need t use same input as as for 'gage' call
analysis.esg.up <- esset.grp(analysis.1$greater,data.G1, gsets =kegg.gs, ref = ans.ref, samp = ans.samp,test4up = T, same.dir=ans.same.dir, output = T, outname = "test", make.plot = T, compare = ans.compare)
names(kegg.gs)
names(analysis.esg.up)
analysis.esg.up$setGroups

head(analy)