Initial analysis, differential expression data
========================================================
Created: Oct 7, 2013, Bryan Linggi  
 
input: prerocessed data . load R.data from diagnostics folder
output: plots to identify general trends or problems in data    

executed: `r date() `  

```{r}
setwd('/Volumes/Documents-1/R_onAir/EGF_gage analysis/')
require(gplots)
load(file='diagnostics/Preproc.Rdata')
# check correlation between pairs of replicates using scatter plot
pairs(ws, cex.labels=.5, pch=20)
# check correlation using cor

heatmap.2(cor(ws),trace='none')
```
* replicates have high correlation (could do cor function also)  
  
* need to relable the 'low.none.none' to 'low.ctrl.none'  

```{r} 
colnames(ws)
colnames(ws)[1]='low.ctrl.none.1'
colnames(ws)
```
### Perform some tests between conditions   
```{r}
mean.low.ctrl.none = rowMeans(ws[,grep('low.ctrl.none',colnames(ws))])
mean.low.egf.none = rowMeans(ws[,grep('low.egf.none',colnames(ws))])
mean.low.egf.inh = rowMeans(ws[,grep('low.egf.inh',colnames(ws))])

#mean.low.ctrl.inh = rowMeans(ws[,grep('low.ctrl.inh',colnames(ws))])--control was not done
#plot(ws[,1],ws[,7])
plot(mean.low.ctrl.none,mean.low.egf.none, main='EGF effect on low density')
```

### Output   
use ws files still
```{r} 
  save.image('/Volumes/Documents-1/R_onAir/EGF_gage analysis/tests/init_analysis_output.Rdata')
